### 2013-10-15 articles/Proposal-wsclean/paper-proposal-fast-widefield-imager.tex

\begin{figure*}[bh]
\begin{center}
\includegraphics[width=12cm]{EoR0-apparent.png}
\caption{A deep MWA image of EoR0 created from one hour of observing, imaged and deconvolved with WSClean in about an hour using 10 nodes on Fornax. Image has not been beam corrected. Noise level after correcting is 7 mJy.}
\label{fig:stddev-spectrum}
\end{center}
\end{figure*}

\begin{table}
\caption{Data sets envisioned to be used in publication} \label{tbl:observations}
 \begin{tabular}{|c|l|p{6cm}|}
 \hhline{|=|=|=|}
 \textbf{Observatory} & \textbf{Description} & \textbf{Reasons} \\
 \textbf{+ date} & & \\
 \hhline{|=|=|=|}
  2013-05-02 & Decl -55          & $\bullet$ Test imaging at different frequencies\\
  MWA 128T   & GLEAM test data   & $\bullet$ Show computational performance \\
             &                   & \hspace{5mm} at elevation $\sim 60$\\
             &                   & $\bullet$ Full-sky imaging \\
 \hline
  2013-05-16 & Vela and Puppis A & $\bullet$ Test cleaning of diffuse structure \\
  MWA 128T   &                   & $\bullet$ Show computational performance \\
             &                   & \hspace{5mm} of cleaning\\
             &                   & $\bullet$ Pointed observations \\
 \hline
  2013-07-31 & EoR0              & $\bullet$ Test cleaning of point sources \\
  MWA 128T   &                   & $\bullet$ Test deep imaging \\
 \hline
  ---        & Simulations       & $\bullet$ Validate photometry / astrometry \\
             &                   & $\bullet$ Test computational performance \\
             &                   & \hspace{5mm} at very low elevation\\
 \hhline{|=|=|=|}
\end{tabular}
\end{table}

>>>>

\begin{figure*}[bh]
\begin{center}
\includegraphics[width=12cm]{EoR0-apparent.png}
\caption{A deep MWA image of EoR0 created from one hour of observing, imaged and deconvolved with WSClean in about an hour using 10 nodes on Fornax. Image has not been beam corrected. Noise level after correcting is 7 mJy. 200 sources were subtracted from the centre before imaging.}
\label{fig:stddev-spectrum}
\end{center}
\end{figure*}

\begin{table}
\caption{Data sets envisioned to be used in publication} \label{tbl:observations}
 \begin{tabular}{|c|l|p{6cm}|}
 \hhline{|=|=|=|}
 \textbf{Observatory} & \textbf{Description} & \textbf{Reasons} \\
 \textbf{+ date} & & \\
 \hhline{|=|=|=|}
  2013-05-02 & Decl -55          & $\bullet$ Test imaging at different frequencies\\
  MWA 128T   & GLEAM test data   & $\bullet$ Show computational performance \\
             &                   & \hspace{5mm} at elevation $\sim 60$\\
             &                   & $\bullet$ Full-sky imaging \\
 \hline
  2013-05-16 & Vela and Puppis A & $\bullet$ Test cleaning of diffuse structure \\
  MWA 128T   &                   & $\bullet$ Show computational performance \\
             &                   & \hspace{5mm} of cleaning\\
             &                   & $\bullet$ Pointed observations \\
 \hline
  2013-07-31 & EoR0              & $\bullet$ Test cleaning of point sources \\
  MWA 128T   &                   & $\bullet$ Test deep imaging \\
 \hline
  2008-2009  & ZCosmos           & $\bullet$ Test relevance to GMRT data \\
  GMRT       & (stacking)        & $\bullet$ Verify making image cubes \\
 \hline
  LOFAR      & To be determined  & $\bullet$ Test relevance to LOFAR data \\
             &                   & (only if data easily obtainable) \\
 \hline
             & Simulations       & $\bullet$ Validate photometry / astrometry \\
   ---       &                   & $\bullet$ Test computational performance \\
             &                   & \hspace{5mm} at very low elevation\\
 \hhline{|=|=|=|}
\end{tabular}
\end{table}
